Supporting Information

### 2017-06-12 code/rmarkdown/figures.Rmd
assorted improvements based on reviewer's suggestions

```{r, echo = FALSE, fig.height = 1.9, fig.width = column_width, fig.cap = paste0("Prioritizations for the first case study. Polygons denote planning units. Dark green planning units were selected for protection. Panel (a) shows the solution generated when using ",cs1_parameters$amount_target*100," % amount targets. Panel (b) shows the solution when using ", cs1_parameters$amount_target*100, " % amount targets and ", cs1_parameters$space_target*100, " % niche targets.")}
# prepare data
cs1_pus_sel_fpolygons <- plyr::ldply(
  names(cs1_prioritisations),
  function(x) {
    curr_data <- cs1_pus_fpolygons
    curr_data$Prioritisation <- x
    curr_data$Solution <- "discarded"
    curr_pus <- which(as.logical(raptr::selections(cs1_prioritisations[[x]])))
    curr_data$Solution[curr_data$id %in% curr_pus] <- "selected"
    return(curr_data)
  }
)
cs1_pus_sel_fpolygons$Prioritisation <- factor(as.character(
  cs1_pus_sel_fpolygons$Prioritisation),
  levels = names(cs1_prioritisations))
# make letter data.frame
cs1_pus_sel_letters_data <- data.frame(
  x = unname(cs1_pus@bbox[1,1] + (diff(cs1_pus@bbox[1, ]) * 0.08)),
  y = unname(cs1_pus@bbox[2,1] + (diff(cs1_pus@bbox[2, ]) * 0.95)),
  Prioritisation = names(cs1_prioritisations),
  letter = paste0("(", letters[1:2], ")"))
# make plots
ggplot2::ggplot() +
  ggplot2::geom_polygon(data=aus_fpolygons,
                        ggplot2::aes(x=long, y=lat, group=group),
                        fill = "grey85", color = "grey70", size = 0.05) +
  ggplot2::geom_polygon(data = cs1_pus_sel_fpolygons,
                        ggplot2::aes(x = long, y = lat, group = group,
                                    fill = Solution),
                        color = "black", size = 0.05) +
  ggplot2::geom_label(data = cs1_pus_sel_letters_data,
                      ggplot2::aes(label = letter, x = x, y = y),
                      color = "black", fill = scales::alpha("white", 0.8),
                                                             size=3) +
  ggplot2::theme_classic() +
  ggplot2::theme(
    axis.ticks = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    plot.margin = ggplot2::unit(c(0, 0, 0, 0), "lines"),
    strip.background = ggplot2::element_rect(fill = "grey20"),
    strip.text = ggplot2::element_text(color = "white", size = 8),
    axis.title = ggplot2::element_blank(),
    legend.position = "none") +
  ggplot2::scale_fill_manual(name = "Solution",
                             values = c("discarded"="#f7fcfd",
                                        "selected"="#00441b")) +
  ggplot2::coord_cartesian(xlim = buffered_range(cs1_pus@bbox[1, ], 0.025),
                           ylim = buffered_range(cs1_pus@bbox[2, ], 0.025),
                           expand = FALSE) +
  ggplot2::facet_wrap(~ Prioritisation, ncol = 2)
```

@@

```{r, echo = FALSE, fig.height = 2.5, fig.width = column_width, fig.cap = paste0("Prioritizations for the second case study. Panels (a--b) show prioritizations generated using different parameters. Polygons denote planning units. Dark green planning units were selected for protection. Panel (a) shows the planning units selected when using ",cs2_parameters$amount_target * 100," % amount targets. Panel (b) shows the planning units selected when using ",cs2_parameters$amount.target*100," % amount targets and ",cs2_parameters$genetic_target * 100," % genetic targets. Panels (c--d) show the solutions in the genetic space. Each point corresponds to a planning unit. The coordinates of the points represent the typical genetic characteristics of individuals sampled in that planning unit (based on an NMDS of the binary loci data). Planning units associated with points that are closer together contain individuals with more similar genetic characteristics than planning units that are further apart.")}
# prepare spatial data
cs2_sel_grid_sub_fpolygons <- cs2_grid_sub_fpolygons
cs2_sel_grid_sub_fpolygons$Title1 <-"Amount target"
cs2_sel_grid_sub_fpolygons$Title2 <- "Amount & genetic target"

>>>>

```{r, echo = FALSE, fig.height = 1.9, fig.width = column_width, fig.cap = paste0("Prioritizations for the first case study. Polygons denote planning units. Dark green planning units were selected for protection. Panel (a) shows the solution generated when using ",cs1_parameters$amount_target*100," % amount targets. Panel (b) shows the solution when using ", cs1_parameters$amount_target*100, " % amount targets and ", cs1_parameters$space_target*100, " % space targets.")}
# prepare data
cs1_pus_sel_fpolygons <- plyr::ldply(
  names(cs1_prioritisations),
  function(x) {
    curr_data <- cs1_pus_fpolygons
    curr_data$Prioritisation <- x
    curr_data$Solution <- "discarded"
    curr_pus <- which(as.logical(raptr::selections(cs1_prioritisations[[x]])))
    curr_data$Solution[curr_data$id %in% curr_pus] <- "selected"
    return(curr_data)
  }
)
cs1_pus_sel_fpolygons$Prioritisation <- factor(as.character(
  cs1_pus_sel_fpolygons$Prioritisation),
  levels = names(cs1_prioritisations))
# make letter data.frame
cs1_pus_sel_letters_data <- data.frame(
  x = unname(cs1_pus@bbox[1,1] + (diff(cs1_pus@bbox[1, ]) * 0.08)),
  y = unname(cs1_pus@bbox[2,1] + (diff(cs1_pus@bbox[2, ]) * 0.95)),
  Prioritisation = names(cs1_prioritisations),
  letter = paste0("(", letters[1:2], ")"))
# make plots
ggplot2::ggplot() +
  ggplot2::geom_polygon(data=aus_fpolygons,
                        ggplot2::aes(x=long, y=lat, group=group),
                        fill = "grey85", color = "grey70", size = 0.05) +
  ggplot2::geom_polygon(data = cs1_pus_sel_fpolygons,
                        ggplot2::aes(x = long, y = lat, group = group,
                                    fill = Solution),
                        color = "black", size = 0.05) +
  ggplot2::geom_label(data = cs1_pus_sel_letters_data,
                      ggplot2::aes(label = letter, x = x, y = y),
                      color = "black", fill = scales::alpha("white", 0.8),
                                                             size=3) +
  ggplot2::theme_classic() +
  ggplot2::theme(
    axis.ticks = ggplot2::element_blank(),
    axis.text = ggplot2::element_blank(),
    axis.line = ggplot2::element_blank(),
    plot.margin = ggplot2::unit(c(0, 0, 0, 0), "lines"),
    strip.background = ggplot2::element_rect(fill = "grey20"),
    strip.text = ggplot2::element_text(color = "white", size = 8),
    axis.title = ggplot2::element_blank(),
    legend.position = "none") +
  ggplot2::scale_fill_manual(name = "Solution",
                             values = c("discarded"="#f7fcfd",
                                        "selected"="#00441b")) +
  ggplot2::coord_cartesian(xlim = buffered_range(cs1_pus@bbox[1, ], 0.025),
                           ylim = buffered_range(cs1_pus@bbox[2, ], 0.025),
                           expand = FALSE) +
  ggplot2::facet_wrap(~ Prioritisation, ncol = 2)
```

@@

```{r, echo = FALSE, fig.height = 2.5, fig.width = column_width, fig.cap = paste0("Prioritizations for the second case study. Panels (a--b) show prioritizations generated using different parameters. Polygons denote planning units. Dark green planning units were selected for protection. Panel (a) shows the planning units selected when using ",cs2_parameters$amount_target * 100," % amount targets. Panel (b) shows the planning units selected when using ",cs2_parameters$amount.target*100," % amount targets and ",cs2_parameters$genetic_target * 100," % space targets. Panels (c--d) show the solutions in the genetic space. Each point corresponds to a planning unit. The coordinates of the points represent the typical genetic characteristics of individuals sampled in that planning unit (based on an NMDS of the binary loci data). Planning units associated with points that are closer together contain individuals with more similar genetic characteristics than planning units that are further apart.")}
# prepare spatial data
cs2_sel_grid_sub_fpolygons <- cs2_grid_sub_fpolygons
cs2_sel_grid_sub_fpolygons$Title1 <-"Amount target"
cs2_sel_grid_sub_fpolygons$Title2 <- "Amount & genetic target"

### 2017-06-12 code/rmarkdown/supporting-information.Rmd
assorted improvements based on reviewer's suggestions

# Figures
```{r, echo = FALSE, fig.height = 8, fig.width = 8.5, fig.cap = "Attribute spaces used in the first case-study. Each panel shows a the distribution of a solution in environmental space and how it samples the realized niche for a different species. The left column of panels shows the solution generated using amount targets. The right column of panels shows the solution generated using amount and niche targets. Each column of panels corresponds to a different species. Hexagons show the distribution of demand points. The color of each hexagon denotes the weighted frequency of demand points inside it. Points represent the environmental conditions associated with planning units inside the species geographic range that were selected for preservation in a given solution."}
## prepare data
cs1_pu_niche_data <- plyr::ddply(cs1_spp_results,
  c("Species", "Prioritisation"),
  function(x) {
    # init
    curr_prioritisation <- cs1_prioritisations[[as.character(x$Prioritisation)]]
    curr_spp_pos <- match(x$Species[1], curr_prioritisation@data@species[[1]])
    curr_ids <- curr_prioritisation %>%
                slot("data") %>%
                slot("attribute.spaces") %>%
                `[[`(1) %>%
                slot("spaces") %>%
                `[[`(curr_spp_pos) %>%
                slot("planning.unit.points") %>%
                slot("ids")
    curr_sel_pos <- which(curr_ids %in% which(as.logical(
                          raptr::selections(curr_prioritisation))))
    # extract planning units
    curr_data <- curr_prioritisation %>%
                slot("data") %>%
                slot("attribute.spaces") %>%
                `[[`(1) %>%
                slot("spaces") %>%
                `[[`(curr_spp_pos) %>%
                slot("planning.unit.points") %>%
                slot("coords") %>%
                as.data.frame() %>%
                magrittr::set_names(c("Niche1", "Niche2")) %>%
                dplyr::mutate(Species = x[["Species"]][[1]],
                              Prioritisation = x[["Prioritisation"]][[1]],
                              Solution <- "discarded")
    curr_data$Solution[curr_sel_pos] <- "selected"
    # return data
    return(curr_data)
})
cs1_pu_niche_data %<>% dplyr::filter(Solution == "selected")

cs1_dp_niche_data <- plyr::ddply(
  cs1_spp_results,
  c("Species", "Prioritisation"),
  function(x) {
    # init
    curr_prioritisation <- cs1_prioritisations[[as.character(x$Prioritisation)]]
    curr_spp_pos <- match(x$Species[1], curr_prioritisation@data@species[[1]])
    # extract demand points
    curr_data <- curr_prioritisation %>%
                  slot("data") %>%
                  slot("attribute.spaces") %>%
                  `[[`(1) %>%
                  slot("spaces") %>%
                  `[[`(curr_spp_pos) %>%
                  slot("demand.points") %>%
                  slot("coords") %>%
                  as.data.frame() %>%
                  magrittr::set_names(c("Niche1", "Niche2"))
    curr_data$weight <- curr_prioritisation %>%
                        slot("data") %>%
                        slot("attribute.spaces") %>%
                        `[[`(1) %>%
                        slot("spaces") %>%
                        `[[`(curr_spp_pos) %>%
                        slot("demand.points") %>%
                        slot("weights")
    # return data
    return(curr_data)
})
cs1_pu_niche_data$Prioritisation <- factor(as.character(
                                      cs1_pu_niche_data$Prioritisation),
                                      levels = names(cs1_prioritisations))
cs1_dp_niche_data$Prioritisation <- factor(as.character(
                                      cs1_dp_niche_data$Prioritisation),
                                      levels = names(cs1_prioritisations))

>>>>

# Figures
```{r, echo = FALSE, fig.height = 8, fig.width = 8.5, fig.cap = "Attribute spaces used in the first case-study. Each panel shows a the distribution of a solution in environmental space and how it samples the realized niche for a different species. The left column of panels shows the solution generated using amount targets. The right column of panels shows the solution generated using amount and space targets. Each column of panels corresponds to a different species. Hexagons show the distribution of demand points. The color of each hexagon denotes the weighted frequency of demand points inside it. Points represent the environmental conditions associated with planning units inside the species geographic range that were selected for preservation in a given solution."}
## prepare data
cs1_pu_niche_data <- plyr::ddply(cs1_spp_results,
  c("Species", "Prioritisation"),
  function(x) {
    # init
    curr_prioritisation <- cs1_prioritisations[[as.character(x$Prioritisation)]]
    curr_spp_pos <- match(x$Species[1], curr_prioritisation@data@species[[1]])
    curr_ids <- curr_prioritisation %>%
                slot("data") %>%
                slot("attribute.spaces") %>%
                `[[`(1) %>%
                slot("spaces") %>%
                `[[`(curr_spp_pos) %>%
                slot("planning.unit.points") %>%
                slot("ids")
    curr_sel_pos <- which(curr_ids %in% which(as.logical(
                          raptr::selections(curr_prioritisation))))
    # extract planning units
    curr_data <- curr_prioritisation %>%
                slot("data") %>%
                slot("attribute.spaces") %>%
                `[[`(1) %>%
                slot("spaces") %>%
                `[[`(curr_spp_pos) %>%
                slot("planning.unit.points") %>%
                slot("coords") %>%
                as.data.frame() %>%
                magrittr::set_names(c("Niche1", "Niche2")) %>%
                dplyr::mutate(Species = x[["Species"]][[1]],
                              Prioritisation = x[["Prioritisation"]][[1]],
                              Solution <- "discarded")
    curr_data$Solution[curr_sel_pos] <- "selected"
    # return data
    return(curr_data)
})
cs1_pu_niche_data %<>% dplyr::filter(Solution == "selected")

cs1_dp_niche_data <- plyr::ddply(
  cs1_spp_results,
  c("Species", "Prioritisation"),
  function(x) {
    # init
    curr_prioritisation <- cs1_prioritisations[[as.character(x$Prioritisation)]]
    curr_spp_pos <- match(x$Species[1], curr_prioritisation@data@species[[1]])
    # extract demand points
    curr_data <- curr_prioritisation %>%
                  slot("data") %>%
                  slot("attribute.spaces") %>%
                  `[[`(1) %>%
                  slot("spaces") %>%
                  `[[`(curr_spp_pos) %>%
                  slot("demand.points") %>%
                  slot("coords") %>%
                  as.data.frame() %>%
                  magrittr::set_names(c("Niche1", "Niche2"))
    curr_data$weight <- curr_prioritisation %>%
                        slot("data") %>%
                        slot("attribute.spaces") %>%
                        `[[`(1) %>%
                        slot("spaces") %>%
                        `[[`(curr_spp_pos) %>%
                        slot("demand.points") %>%
                        slot("weights")
    # return data
    return(curr_data)
})

cs1_pu_niche_data$Prioritisation[grepl("niche", as.character(cs1_pu_niche_data$Prioritisation))] <- "Amount & space targets"

cs1_dp_niche_data$Prioritisation[grepl("niche", as.character(cs1_dp_niche_data$Prioritisation))] <- "Amount & space targets"

cs1_pu_niche_data$Prioritisation <- factor(cs1_pu_niche_data$Prioritisation, levels = rev(unique(cs1_pu_niche_data$Prioritisation)))

cs1_dp_niche_data$Prioritisation <- factor(cs1_dp_niche_data$Prioritisation, levels = rev(unique(cs1_dp_niche_data$Prioritisation)))
